\documentclass[preprint, 11pt]{elsarticle}
%\documentclass[final, 3p, 10pt]{elsarticle}

\usepackage[bitstream-charter]{mathdesign}      % nice font
\usepackage{amsmath}                            % lots of math typesetting
\usepackage{tikz}                               % pretty pictures
\usepackage{mathtools}                          % used for ceiling command
\usepackage{booktabs}                           % pretty tables
\usepackage{algorithm2e}                        % nice algorithms
\usepackage{imakeidx}                           % nice indexing
\usepackage{amsfonts}                           % special characters
\usepackage{listings}                           % to display code snippets
\usepackage{xspace}                             % helps spacing for \Detran
\usepackage[refpage]{nomencl}                   %
\usepackage{subcaption}
\usepackage{lscape}
\usepackage{threeparttable}
%\usepackage{fullpage}

\journal{Annals of Nuclear Energy}

\newcommand{\Detran}{{\tt Detran}\xspace}
\newcommand{\Serment}{{\tt Serment}\xspace}
\newcommand{\ie}{{\it i.e.}\xspace}
\newcommand{\eg}{{\it e.g.}\xspace}
\newcommand{\transp}{\mathsf{T}}
% Other helpful macros
\newcommand{\oper}[1]{\mathbf{#1}}

\begin{document}

\begin{frontmatter}

\title{Solving Eigenvalue Response Matrix Equations with 
       Nonlinear Techniques}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[label1]{Jeremy A. Roberts\corref{cor1}}
\author[label2]{Benoit Forget}
\address[label1]{Department of Mechanical and Nuclear Engineering,
                 Kansas State University, 3002 Rathbone Hall, Manhattan, KS 66506, USA}
\address[label2]{Department of Nuclear Science and Engineering, 
                 Massachusetts Institute of Technology,
                 77 Massachusetts Avenue, 24-107, Cambridge, MA 02139, USA}
\cortext[cor1]{Corresponding author; email address: jaroberts@ksu.edu.}

\begin{abstract}
%% Text of abstract

This paper presents new algorithms for use in 
the eigenvalue response matrix method (ERMM) for reactor 
eigenvalue problems.  ERMM spatially decomposes a
 domain into independent nodes linked via
 boundary conditions approximated as 
truncated orthogonal expansions, the coefficients of which are  
response functions. 
In its simplest form, ERMM consists of a two-level 
eigenproblem: an outer Picard iteration updates the $k$-eigenvalue 
via balance,
while the inner $\lambda$-eigenproblem imposes neutron balance between nodes.  
Efficient methods are developed for solving the inner $\lambda$-eigenvalue 
problem within the outer Picard iteration. 
 Based on results from  
several diffusion and transport benchmark models, it was found that 
the Krylov-Schur method 
applied to the $\lambda$-eigenvalue problem reduces Picard solver 
times (excluding response generation) by a factor of 2--5. 
Furthermore, alternative methods including Picard acceleration schemes, Steffensen's 
method, and Newton's method are developed.  These approaches can 
yield faster $k$ convergence and a need for fewer
 $k$-dependent response function evaluations,
important because response computation is the 
largest cost for many problems.  It was found that
accelerating Picard iteration yields a reduction of 2--3 in total time 
compared to the unaccelerated case
for problems dominated by response generation but that 
Newton's method may provide nearly the same performance with improved 
robustness.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
response matrix \sep reactor physics \sep neutron transport \sep eigenvalue
\end{keyword}

\end{frontmatter}

\input{nonlinear_erme_content}


%% References with bibTeX database:
\bibliographystyle{elsarticle-num}
\bibliography{robertsj_thesis.bib}
%\bibliographystyle{unsrt}


\end{document}

\begin{abstract}

\end{abstract}

\include{nonlinear_erme_content}

\end{document}
